\section{Conclusions}
When the TCP/IP protocol stack was first developed in the early 1980s, the goal was to connect mainframe computers through the wired connectivity. Although the protocol stack kept evolving after the IP specification was published, the fundamental assumption behind the architecture design has not changed.\par
For the last 40 years, the current Internet system struggles with enabling a secure communication between hosts.
IoT networks and its applications show that traditional networking is not going to work well with the functionalities required by IoT devices. For this purpose we discussed the ICN Stack which provides the IoT environment all its functionalities with security and privacy as well. \par
However having discussed this, traditional IP stack are with us for the foreseeable future, and ICN stack is not meant to be a replacement for it. But ICN stacks can work in conjunction to the current Internet systems ans especially the upcoming IoT systems. And therefore the ICN designs must be implemented alongside.\par 
In this report we discussed thoroughly about the IoT requirements and how ICN provides the networkinf functionalities that it requires. We also looked into the middleware architecture that provides a good administrative structure that provides the ICN functionalities efficiently.This middleware focuses mainly on security and privacy of the overall system. Then we went on to discuss about the individual functionalities and how they provide integrity, confidentiality, authenticity and authorization. After this we discussed some of the ongoing discussions in the Internet community realted to ICNs. \par
ICN has been very recently addressing these security issues and still requires some time until it is fully integrated in our technology. Therefore it is of utmost importance to ensure a proper security and privacy measures to be introduced in the early stages of network design. This is one such proposal that will ensure the security functionalities required for secure communication. Eventually we would expect to see the change in the Internet paradigm and a shift towards ICN.
